%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeProjItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumetiItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-55pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeProjItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/akshayrdeodhar}{\Large Akshay Deodhar}} & Email : \href{mailto:adeodhar9@gatech.edu}{adeodhar9@gatech.edu}\\
  \href{https://www.github.com/akshayrdeodhar}{github.com/akshayrdeodhar}, \href{https://akshayrdeodhar.github.io}{akshayrdeodhar.github.io} & Mobile : +1 (470) 659-7798 \\
\end{tabular*}

\vspace{-10pt}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Master of Science in Computer Science; Specialization: Computing Systems}{Aug. 2021 -- June 2023}
      \vspace{-5pt}
    \resumeSubheading
      {College of Engineering Pune}{Pune, India}
      {Honours Bachelor of Technology in Computer Engineering;  GPA: 3.82 (9.56/10.0)}{Jul. 2017 -- June. 2021}
      \vspace{-7pt}
  \resumeSubHeadingListEnd

\vspace{-7pt}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading {Veritas Technologies}{Pune, India}
      {Software Engineer Intern}{Jan 2021 - July 2021}
      \resumeItemListStart
            \resumeItem{Veritas Infoscale is a high-performance enterprise storage management solution built on top of Veritas's Cluster File System (CFS) and Volume Manager (CVM).}
   	        \resumeItem{Enhanced Infoscale's Container Storage Interface (CSI) plugin, to support \textbf{volume provisioning} for pods in large \textbf{Kubernetes}
   	           clusters spanning multiple Infoscale storage clusters. Original plugin supports single storage cluster.}
   	           \vspace{-11pt}
            \resumeItem{Supported a federation of storage clusters in Kubernetes by creating Custom Resources for storing federation and volume metadata, and writing a controller (operator) for dynamic federation membership management.}
            
            \resumeItem{Worked with a wide range of languages and tools including Golang, Python, operator-sdk, Custom Resources, Secrets, K8s API clients and REST APIs.}
		
		\resumeItemListEnd
        
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {IIT Kanpur}{Kanpur, India}
      {Research Intern}{Dec 2019 -- Aug 2020}
      \resumeItemListStart
      \resumeItem{Sparse Matrix-Vector Multiplication (SpMV) is a linear algebra kernel
		whose performance varies significantly with the sparse matrix storage format
		and processor architecture.}
		\resumeItem{Worked on \textbf{automatic format selection for SpMV on GPUs}, with a focus on
		portability and training cost, leading to a publication in
		the DUAC workshop  at ICPP 2021.}
		\resumeItem{Developed a semi-supervised format predictor that achieves \textbf{83\%} accuracy 
		while requiring format labeling for just \textbf{10\%} of the training set matrices. Reduced training time by ~\textbf{80\%}}.
        \resumeItem{Designed and implemented sampling algorithms for predicting the optimal sparse matrix
		format by analyzing the Nvidia CUDA CUSP SpMV kernels,
        improving accuracy by \textbf{30\%}.}
	\resumeItemListEnd

    \resumeSubheading{ISRO COEP Satellite Initiative}{Pune, India}
      {Subsystem Lead and Individual Contributor}{Nov 2017 -- June 2021}
      \resumeItemListStart
         \resumeItem{Led and mentored a \textbf{multidisciplinary} team of \textbf{8} engineering students in designing an Attitude Determination and Control Subsystem (ADCS) for a \textbf{solar sailing satellite}.}
		\resumeItem{ Developed and validated an \textbf{orbit simulation} for the satellite using NASA's General Mission Analysis Tool (GMAT) and its Python API.}
        \resumeItem{Added modules for calculating optimal solar sail orientations for orbit raising and for modeling non-ideal actuator behavior to a C-based Runge-Kutta 4 numerical satellite attitude dynamics simulation.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd
  
\vspace{-7pt}
  
\section{Publications}
    \resumeSubHeadingListStart
        \resumeItem{}{Sunidhi Dhandhania, \textbf{Akshay Deodhar}, \textit{et. al.} ``Explaining the Performance of Supervised and Semi-Supervised Methods for Automated Sparse Matrix Format Selection''. \textit{International Workshop on Deployment and Usage of Accelerators, ICPP} 2021, Chicago, USA}
        \vspace{-5pt}
        \resumeItem{}{\textbf{Akshay Deodhar}, Aditya Neralkar, \textit{et. al.}  ``Analysis of Solar Sailing as a Means of Orbit Maneuvering for Nanosatellites in Low Earth Orbit''. \textit{International Astronautical Congress}, 2019, Washington DC, USA}
        
        \resumeItemListEnd

\vspace{-7pt}

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{xv6 threads}{Added clone, join, park and unpark syscalls to the \textbf{xv6 kernel} to support threading and semaphores.}
    \resumeSubItem{CaSH}{Unix shell that supports multiple pipes, redirection and job control. Extensive use of system calls and signals.}
    \resumeSubItem{RankRecommend}{GitHub follow recommendations using a modified version of PageRank on the follow graph.}
    \resumeSubItem{Trillian}{Command-line chess game that with a minmax AI and $\alpha$-$\beta$ pruning. Uses a legal move cache for efficiency.}
    \resumeSubItem{bookFlow}{Django app to connect students across years and eliminate middlemen from the used textbooks market.}
\resumeSubHeadingListEnd

\vspace{-7pt}
%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{C, Python, Go (Golang), C++, CUDA, Scheme, Bash}
    \resumeSubItem{Technologies}{Kubernetes, Linux, Gdb, Git, Valgrind, scikit-learn, Scipy, openSSL, Docker, Django, Flask, gRPC}
    \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
